---
title: "Exact Solution Model Area"
author: "Shawn Gilroy"
date: "October 22, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache = TRUE,
                      fig.path = "plots/",
                      dev = c("png"),
                      dpi = 500)

require(ggplot2)
require(grid)
require(gridExtra)
require(dplyr)
require(tidyr)
require(knitr)

#devtools::install_github("miyamot0/discountingtools")
require(discountingtools)

#file <- read.csv("Sim Comparisons.csv", stringsAsFactors = FALSE)

mVars = read.csv("Sim Comparisons.csv", stringsAsFactors = FALSE)

```

### Table 1. Relationships between measures

``` {r, SimulationResults, echo=FALSE, warning=FALSE, results="asis"}

tableDiffs <- mVars %>%
  summarise(Model = "Overall",
            W = wilcox.test(NI.AUC, Exact.AUC, correct = FALSE)$statistic,
            p = wilcox.test(NI.AUC, Exact.AUC, correct = FALSE)$p.value,
            rho = cor.test(NI.AUC, Exact.AUC, method="spearman")$estimate)

tableDiffsByModel <- mVars %>%
  group_by(Model) %>%
  summarise(W = wilcox.test(NI.AUC, Exact.AUC, correct = FALSE)$statistic,
            p = wilcox.test(NI.AUC, Exact.AUC, correct = FALSE)$p.value,
            rho = cor.test(NI.AUC, Exact.AUC, method="spearman")$estimate)

tableDiffsAll <- rbind(tableDiffs, tableDiffsByModel)

kable(tableDiffsAll)

```

This table provides the results from exact solution MB-AUC. The MB-AUC area measure is derived from two delays of interest (T1 = 7; T2 = 1825), the maximum value of the commodity (A), and the fitted model parameters.

### Figure 1

```{r, Figure_1, echo=FALSE, warning=FALSE, cache=TRUE, fig.align="center", fig.height=5, fig.width=9 }
xLabels <- c(1,NA,NA,365,1825,3650, NA, NA)
xLabels2 <- c(1,NA,NA,365,1825,3650, 7300, NA)
xLabels3 <- c(1,NA,NA,365,1825,3650, 7300, 14600)

xDelays <- c(1,30,180,365,1825,3650, 7300, 14600)

dataFrame <- data.frame(X=xDelays,
                        Y=c(945,855,845,750,636,274,NA,NA))

dataFrame2 <- data.frame(X=xDelays,
                         Y=c(945,855,845,750,636,274,274,NA))

dataFrame3 <- data.frame(X=xDelays,
                         Y=c(945,855,845,750,636,274,274,274))

annotateMessage = sprintf("Maximum Area = (%s - %s) * 1000 = %s", 3650, 1, (3650-1) * 1000)

plotDraw <- ggplot(dataFrame, aes(x=X, y=Y, fill="gray")) +
  geom_line(size=1, linetype=1) +
  geom_area() +
  geom_point() +
  scale_fill_manual(values = c('gray')) +
  geom_segment(aes(x = dataFrame$X[1], y = 0, xend = dataFrame$X[1], yend = dataFrame$Y[1], colour = "black")) +
  geom_segment(aes(x = dataFrame$X[2], y = 0, xend = dataFrame$X[2], yend = dataFrame$Y[2], colour = "black")) +
  geom_segment(aes(x = dataFrame$X[3], y = 0, xend = dataFrame$X[3], yend = dataFrame$Y[3], colour = "black")) +
  geom_segment(aes(x = dataFrame$X[4], y = 0, xend = dataFrame$X[4], yend = dataFrame$Y[4], colour = "black")) +
  geom_segment(aes(x = dataFrame$X[5], y = 0, xend = dataFrame$X[5], yend = dataFrame$Y[5], colour = "black")) +
  geom_segment(aes(x = dataFrame$X[6], y = 0, xend = dataFrame$X[6], yend = dataFrame$Y[6], colour = "black")) +
  geom_segment(aes(x = dataFrame$X[7], y = 0, xend = dataFrame$X[7], yend = dataFrame$Y[7], colour = "black")) +
  geom_segment(aes(x = dataFrame$X[8], y = 0, xend = dataFrame$X[8], yend = dataFrame$Y[8], colour = "black")) +
  scale_x_continuous(breaks = xLabels,
                     labels = xLabels,
                     limits = c(0,max(xDelays)),
                     expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,1000), expand = c(0, 0)) +
  annotate("text",
           y = 900,
           x = max(xDelays) - 250,
           label = annotateMessage,
           hjust = 1,
           family = "serif") +
  scale_colour_manual(values = c('black')) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(0.1,0.5,0.1,0.5), "cm"),
        legend.position="none",
        plot.title = element_text(hjust = 0.5),
        axis.text = element_text(color = "black"),
        text=element_text(size=10, family="serif")) +
  labs(title = "PB-AUC = 0.5876 (Max Delay = 3650)",
       x = "",
       y = "")

annotateMessage2 = sprintf("Maximum Area = (%s - %s) * 1000 = %s", 7300, 1, (7300-1) * 1000)

plotDraw2 <- ggplot(dataFrame2, aes(x=X, y=Y, fill="gray")) +
  geom_line(size=1) +
  geom_area(aes(x=X, y=Y, fill="gray"), data = dataFrame2) +
  geom_point() +
  scale_fill_manual(values = c('gray')) +
  geom_segment(aes(x = dataFrame2$X[1], y = 0, xend = dataFrame2$X[1], yend = dataFrame2$Y[1], colour = "black")) +
  geom_segment(aes(x = dataFrame2$X[2], y = 0, xend = dataFrame2$X[2], yend = dataFrame2$Y[2], colour = "black")) +
  geom_segment(aes(x = dataFrame2$X[3], y = 0, xend = dataFrame2$X[3], yend = dataFrame2$Y[3], colour = "black")) +
  geom_segment(aes(x = dataFrame2$X[4], y = 0, xend = dataFrame2$X[4], yend = dataFrame2$Y[4], colour = "black")) +
  geom_segment(aes(x = dataFrame2$X[5], y = 0, xend = dataFrame2$X[5], yend = dataFrame2$Y[5], colour = "black")) +
  geom_segment(aes(x = dataFrame2$X[6], y = 0, xend = dataFrame2$X[6], yend = dataFrame2$Y[6], colour = "black")) +
  geom_segment(aes(x = dataFrame2$X[7], y = 0, xend = dataFrame2$X[7], yend = dataFrame2$Y[7], colour = "black")) +
  geom_segment(aes(x = dataFrame2$X[8], y = 0, xend = dataFrame2$X[8], yend = dataFrame2$Y[8], colour = "black")) +
  scale_x_continuous(breaks = xLabels2,
                     labels = xLabels2,
                     limits = c(0,max(xDelays)),
                     expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,1000), expand = c(0, 0)) +
  annotate("text",
           y = 900,
           x = max(xDelays) - 250,
           label = annotateMessage2,
           hjust = 1,
           family = "serif") +
  scale_colour_manual(values = c('black')) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(0.1,0.5,0.1,0.5), "cm"),
        legend.position="none",
        plot.title = element_text(hjust = 0.5),
        axis.text = element_text(color = "black"),
        text=element_text(size=10, family="serif")) +
  labs(title = "PB-AUC = 0.4306 (Max Delay = 7300)",
       x = "",
       y = "Value")

annotateMessage3 = sprintf("Maximum Area = (%s - %s) * 1000 = %s", 14600, 1, (14600-1) * 1000)

plotDraw3 <- ggplot(dataFrame3, aes(x=X, y=Y, fill="gray")) +
  geom_line(size=1) +
  geom_area(aes(x=X, y=Y, fill="gray"), data = dataFrame3) +
  geom_point() +
  scale_fill_manual(values = c('gray')) +
  geom_segment(aes(x = dataFrame3$X[1], y = 0, xend = dataFrame3$X[1], yend = dataFrame3$Y[1], colour = "black")) +
  geom_segment(aes(x = dataFrame3$X[2], y = 0, xend = dataFrame3$X[2], yend = dataFrame3$Y[2], colour = "black")) +
  geom_segment(aes(x = dataFrame3$X[3], y = 0, xend = dataFrame3$X[3], yend = dataFrame3$Y[3], colour = "black")) +
  geom_segment(aes(x = dataFrame3$X[4], y = 0, xend = dataFrame3$X[4], yend = dataFrame3$Y[4], colour = "black")) +
  geom_segment(aes(x = dataFrame3$X[5], y = 0, xend = dataFrame3$X[5], yend = dataFrame3$Y[5], colour = "black")) +
  geom_segment(aes(x = dataFrame3$X[6], y = 0, xend = dataFrame3$X[6], yend = dataFrame3$Y[6], colour = "black")) +
  geom_segment(aes(x = dataFrame3$X[7], y = 0, xend = dataFrame3$X[7], yend = dataFrame3$Y[7], colour = "black")) +
  geom_segment(aes(x = dataFrame3$X[8], y = 0, xend = dataFrame3$X[8], yend = dataFrame3$Y[8], colour = "black")) +
  scale_x_continuous(breaks = xLabels3,
                     labels = xLabels3,
                     limits = c(0,max(xDelays)),
                     expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,1000), expand = c(0, 0)) +
  annotate("text",
           y = 900,
           x = max(xDelays) - 250,
           label = annotateMessage3,
           hjust = 1,
           family = "serif") +
  scale_colour_manual(values = c('black')) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = unit(c(0.1,0.5,0.1,0.5), "cm"),
        legend.position="none",
        plot.title = element_text(hjust = 0.5),
        axis.text = element_text(color = "black"),
        text=element_text(size=10, family="serif")) +
  labs(title = "PB-AUC = 0.3523 (Max Delay = 14600)",
       x = "Delay",
       y = "")

par(family = "serif", mar=c(3,3,2,1), mgp=c(2,.7,0), tck=-.01)

grid.newpage()
pushViewport(viewport(layout = grid.layout(3, 6,
                                           heights = unit(c(11), "null"),
                                           widths = unit(c(8, 8, 8, 8, 8, 8), "null"))))

print(plotDraw,  vp = viewport(layout.pos.row = 1, layout.pos.col = 1:6))
print(plotDraw2, vp = viewport(layout.pos.row = 2, layout.pos.col = 1:6))
print(plotDraw3, vp = viewport(layout.pos.row = 3, layout.pos.col = 1:6))

```

Note: Examples of how area under curve proportions are affected by both the selection of delay values as well as the degree of discounting. In the subplots above, the overall amount of discounting in each is the same (~75% of value) but the proportion of area under the curve to the maximum area is driven increasingly lower as the maximum delay increases.

### Figure 2

```{r, Figure_2, echo=FALSE, warning=FALSE, cache=TRUE, fig.align="center", fig.height=7, fig.width=9 }
bottomMargin   <- 0.4
leftMarginText <- 0.4
leftMarginBlank<- 0.2
topMargin <- 0.2

par(mfrow = c(2, 1), oma = c(0, 0, 0, 0), mar=c(2, 2, 2, 0) + 0.1, omi=c(0.2,0.2,0,0))

aucDelays <- c(7,14,30,183,365,1825)
aucValues <- c(0.995,0.975,0.825,0.8,0.7,0.6)

hypDelays <- seq(1, 9125, length.out = 20000)
hypValues <- 1 / (1 + 0.002357*hypDelays)

gmDelays <- seq(1, 1825, length.out = 20000)
gmValues <- 1 / (1 + 0.043864*gmDelays)^0.219506

# Base plot, AUC
plot(aucDelays, 
     aucValues,
     main = "Discounting Results as Reported",
     log = "x",
     type = "p",
     cex = 1.5,
     pch = 15,
     xlab = NA,
     ylab = NA,
     xaxt = "n",
     yaxt = "n",
     xlim = c(1, 10000),
     ylim = c(0, 1))

# Axes
atx <- c(1, 10, 100, 1000, 10000)
labels <- sapply(atx, function(i) as.expression(bquote(.(NA))) )
axis(1, at=atx, labels=labels)

aty <- c(0, 0.25, 0.5, 0.75, 1)
labels <- sapply(aty, function(i) as.expression(bquote(.(i))) )
axis(2, at=aty, labels=labels)

# Lines
lines(aucDelays, aucValues)

lines(gmDelays, gmValues, col = "lightgray")

lines(hypDelays, hypValues, col = "darkgray")

# Labels
arrows(1000, 
       0.825, 
       x1 = 1000, 
       y1 = 0.675,
       code = 2)

text(1000, 0.9, labels = c("Study A"))

arrows(500, 
       0.25, 
       x1 = 1000, 
       y1 = 0.25,
       code = 2)

text(450, 0.25, 
     adj = 1,
     labels = c("Study B"))

arrows(10, 
       0.725, 
       x1 = 10, 
       y1 = 0.9,
       code = 2)

text(10, 0.65, labels = c("Study C"))

########################################

aucDelays <- c(7,14,30,183,365,1825)
aucValues <- c(0.995,0.975,0.825,0.8,0.7,0.6)

hypDelays <- seq(7, 1825, length.out = 20000)
hypValues <- 1 / (1 + 0.002357*hypDelays)

gmDelays <- seq(7, 1825, length.out = 20000)
gmValues <- 1 / (1 + 0.043864*gmDelays)^0.219506

# Mod plot, AUC
plot(aucDelays, 
     aucValues,
     main = "Discounting Results with Common Bounds",
     log = "x",
     type = "p",
     cex = 1.5,
     pch = 15,
     xlab = NA,
     ylab = NA,
     xaxt = "n",
     yaxt = "n",
     xlim = c(1, 10000),
     ylim = c(0, 1))

# Axes
atx <- c(1, 10, 100, 1000, 10000)
labels <- sapply(atx, function(i) as.expression(bquote(.(i))) )
axis(1, at=atx, labels=labels)

aty <- c(0, 0.25, 0.5, 0.75, 1)
labels <- sapply(aty, function(i) as.expression(bquote(.(i))) )
axis(2, at=aty, labels=labels)

# Lines
lines(aucDelays, aucValues)

lines(gmDelays, gmValues, col = "lightgray")

lines(hypDelays, hypValues, col = "darkgray")

# Labels
arrows(1000, 
       0.825, 
       x1 = 1000, 
       y1 = 0.675,
       code = 2)

text(1000, 0.9, labels = c("Study A"))

arrows(500, 
       0.25, 
       x1 = 1000, 
       y1 = 0.25,
       code = 2)

text(450, 0.25, 
     adj = 1,
     labels = c("Study B"))

arrows(10, 
       0.725, 
       x1 = 10, 
       y1 = 0.9,
       code = 2)

text(10, 0.65, labels = c("Study C"))

# Description

lines(c(7,7),
      c(-1,10),
      lty = 2)
lines(c(1825,1825),
      c(-1,10),
      lty = 2)

mtext(expression(bold('Normalized Value')), side=2, outer=T, at=0.5)
mtext(expression(bold('Delay')), side=1, line = 2, outer=F, at=100)
```

Note: These two plots in this figure illustrate how modeled discounting processes can be used to focus on specific delays of interests—even if not directly assessed. The top plot shows the discounting data from three hypothetical experiments. In the bottom plot, the range of delays being targeted has been adjusted to match those from the study using PB-AUC (Study A), which cannot be adjusted.

### Figure 3

```{r, Figure_3, echo=FALSE, warning=FALSE, cache=TRUE, fig.align="center", fig.height=7, fig.width=9 }



#overall
#wilcox.test(mVars$NI.AUC, 
#            mVars$Exact.AUC, correct = FALSE)
#cor.test(x=mVars$NI.AUC, 
#         y=mVars$Exact.AUC, method = 'spearman', exact = FALSE)

#Noise
#wilcox.test(mVars[mVars$Model == "Noise",]$NI.AUC, 
#            mVars[mVars$Model == "Noise",]$Exact.AUC, correct = FALSE)
#cor.test(x=mVars[mVars$Model == "Noise",]$NI.AUC, 
#         y=mVars[mVars$Model == "Noise",]$Exact.AUC, method = 'spearman', exact = FALSE)

#Exponential
#wilcox.test(mVars[mVars$Model == "Exponential",]$NI.AUC, 
#            mVars[mVars$Model == "Exponential",]$Exact.AUC, correct = FALSE)
#cor.test(x=mVars[mVars$Model == "Exponential",]$NI.AUC, 
#         y=mVars[mVars$Model == "Exponential",]$Exact.AUC, method = 'spearman', exact = FALSE)

#Hyperbolic
#wilcox.test(mVars[mVars$Model == "Hyperbolic",]$NI.AUC, 
#            mVars[mVars$Model == "Hyperbolic",]$Exact.AUC, correct = FALSE)
#cor.test(x=mVars[mVars$Model == "Hyperbolic",]$NI.AUC, 
#         y=mVars[mVars$Model == "Hyperbolic",]$Exact.AUC, method = 'spearman', exact = FALSE)

#Quasi-Hyperbolic
#wilcox.test(mVars[mVars$Model == "Quasi-Hyperbolic",]$NI.AUC, 
#            mVars[mVars$Model == "Quasi-Hyperbolic",]$Exact.AUC, correct = FALSE)
#cor.test(x=mVars[mVars$Model == "Quasi-Hyperbolic",]$NI.AUC, 
#         y=mVars[mVars$Model == "Quasi-Hyperbolic",]$Exact.AUC, method = 'spearman', exact = FALSE)

#Myerson-Green
#wilcox.test(mVars[mVars$Model == "Myerson-Green",]$NI.AUC, 
#            mVars[mVars$Model == "Myerson-Green",]$Exact.AUC, correct = FALSE)
#cor.test(x=mVars[mVars$Model == "Myerson-Green",]$NI.AUC, 
#         y=mVars[mVars$Model == "Myerson-Green",]$Exact.AUC, method = 'spearman', exact = FALSE)

#Rachlin
#wilcox.test(mVars[mVars$Model == "Rachlin",]$NI.AUC, 
#            mVars[mVars$Model == "Rachlin",]$Exact.AUC, correct = FALSE)
#cor.test(x=mVars[mVars$Model == "Rachlin",]$NI.AUC, 
#         y=mVars[mVars$Model == "Rachlin",]$Exact.AUC, method = 'spearman', exact = FALSE)

#table(file$Model)

fontSize = 3
xOffset = 0.35
yOffset = 0.975

lm_eqn = function(m) {
  
  l <- list(a = as.numeric(format(coef(m)[1], digits = 3)),
            b = as.numeric(format(abs(coef(m)[2]), digits = 3)),
            r2 = format(summary(m)$r.squared, digits = 3));
  
  if (coef(m)[2] >= 0)  {
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2,l)
  } else {
    eq <- substitute(italic(y) == a - b %.% italic(x)*","~~italic(r)^2~"="~r2,l)    
  }
  
  as.character(as.expression(eq));                 
}

par(family = "serif")

plot0 <- ggplot(mVars[mVars$Model == "Noise", c("NI.AUC", "Exact.AUC")], 
                aes(x=NI.AUC, y=Exact.AUC)) + 
  geom_point() +
  geom_smooth(method = "lm", colour = "gray", se = FALSE) +
  theme_bw() +
  annotate("text", 
           x = xOffset, 
           y = yOffset, 
           label = lm_eqn(lm(Exact.AUC ~ NI.AUC, mVars[mVars$Model == "Noise", 
                                                       c("NI.AUC", "Exact.AUC")])), 
           colour="black", 
           size = fontSize, 
           parse=TRUE) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        text=element_text(size=12, family="serif")) +
  labs(title = "Noise Model", 
       x = "",
       y = "Exact Solution Area")

plot1 <- ggplot(mVars[mVars$Model == "Hyperbolic", c("NI.AUC", "Exact.AUC")], aes(x=NI.AUC, y=Exact.AUC)) + 
  geom_point() +
  geom_smooth(method = "lm", colour = "gray", se = FALSE) +
  theme_bw() +
  annotate("text", 
           x = xOffset, 
           y = yOffset, 
           label = lm_eqn(lm(Exact.AUC ~ NI.AUC, mVars[mVars$Model == "Hyperbolic", 
                                                       c("NI.AUC", "Exact.AUC")])), 
           colour="black", 
           size = fontSize, 
           parse=TRUE) +  
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        text=element_text(size=12, family="serif")) +
  labs(title = "Mazur Model",
       x = "",
       y = "Exact Solution Area")

plot2 <- ggplot(mVars[mVars$Model == "Exponential", c("NI.AUC", "Exact.AUC")], aes(x=NI.AUC, y=Exact.AUC)) + 
         geom_point() +
         geom_smooth(method = "lm", colour = "gray", se = FALSE) +
         theme_bw() +
  annotate("text", 
           x = xOffset, 
           y = yOffset, 
           label = lm_eqn(lm(Exact.AUC ~ NI.AUC, mVars[mVars$Model == "Exponential", c("NI.AUC", "Exact.AUC")])), 
           colour="black", 
           size = fontSize, 
           parse=TRUE) +    
         theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
               text=element_text(size=12, family="serif")) +
         labs(title = "Exponential Model",
              x = "",
              y = "Exact Solution Area")

plot3 <- ggplot(mVars[mVars$Model == "Quasi-Hyperbolic", c("NI.AUC", "Exact.AUC")], aes(x=NI.AUC, y=Exact.AUC)) + 
         geom_point() +
         geom_smooth(method = "lm", colour = "gray", se = FALSE) +
         theme_bw() +
  annotate("text", 
           x = xOffset, 
           y = yOffset, 
           label = lm_eqn(lm(Exact.AUC ~ NI.AUC, mVars[mVars$Model == "Quasi-Hyperbolic", c("NI.AUC", "Exact.AUC")])), 
           colour="black", 
           size = fontSize, 
           parse=TRUE) +    
         theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
               text=element_text(size=12, family="serif")) +
         labs(title = "Quasi-Hyperbolic Model", x = "Numerical Integration Area", y = "Exact Solution Area")

plot4 <- ggplot(mVars[mVars$Model == "Myerson-Green", c("NI.AUC", "Exact.AUC")], aes(x=NI.AUC, y=Exact.AUC)) + 
         geom_point() +
         geom_smooth(method = "lm", colour = "gray", se = FALSE) +
         theme_bw() +
  annotate("text", 
           x = xOffset, 
           y = yOffset, 
           label = lm_eqn(lm(Exact.AUC ~ NI.AUC, mVars[mVars$Model == "Myerson-Green", c("NI.AUC", "Exact.AUC")])), 
           colour="black", 
           size = fontSize, 
           parse=TRUE) +      
         theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
               text=element_text(size=12, family="serif")) +
         labs(title = "Green Myerson Model", x = "Numerical Integration Area", y = "Exact Solution Area") 

plot5 <- ggplot(mVars[mVars$Model == "Rachlin", c("NI.AUC", "Exact.AUC")], aes(x=NI.AUC, y=Exact.AUC)) + 
         geom_point() +
         geom_smooth(method = "lm", colour = "gray", se = FALSE) +
         theme_bw() +
  annotate("text", 
           x = xOffset, 
           y = yOffset, 
           label = lm_eqn(lm(Exact.AUC ~ NI.AUC, mVars[mVars$Model == "Rachlin", c("NI.AUC", "Exact.AUC")])), 
           colour="black", 
           size = fontSize, 
           parse=TRUE) +       
         theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
               text=element_text(size=12, family="serif")) +
         labs(title = "Rachlin Model", x = "Numerical Integration Area", y = "Exact Solution Area")

par(family = "serif", mar=c(3,3,2,1), mgp=c(2,.7,0), tck=-.01)

grid.newpage()
pushViewport(viewport(layout = grid.layout(2, 6, heights = unit(c(8, 8), "null"))))

print(plot0, vp = viewport(layout.pos.row = 1, layout.pos.col = 1:2))
print(plot1, vp = viewport(layout.pos.row = 1, layout.pos.col = 3:4))
print(plot2, vp = viewport(layout.pos.row = 1, layout.pos.col = 5:6))

print(plot3, vp = viewport(layout.pos.row = 2, layout.pos.col = 1:2))
print(plot4, vp = viewport(layout.pos.row = 2, layout.pos.col = 3:4))
print(plot5, vp = viewport(layout.pos.row = 2, layout.pos.col = 5:6))

```

Note: These plots depict the relationship between numerical integration and exact solutions for calculating MB-AUC.

### Figure 4

``` {r, Figure_4, echo=FALSE, warning=FALSE, cache=TRUE, fig.align="center", fig.height=6, fig.width=6 }

delayVector <- seq(0, 365, by = 0.1)

# Reynolds et al.

delays <- c(1, 2, 30, 180, 365)
reynoldsSmokers <- c(0.846916079, 0.750327525,0.22421986, 0.098844224, 0.049121418)
reynoldsNonSmokers <- c(0.952414436, 0.950926694, 0.525856007, 0.098844224, 0.150162097)

# Friedel

friedelSmokers <- 1/((1+3.28*delayVector)^0.3)
friedelNonsmokers <- 1/((1+0.004*delayVector)^3.61)

# Bickel

bickelSmokers <- 1/(1+0.05414*delayVector)
bickelNonsmokers <- 1/(1+0.0073*delayVector)

# Mitchell

mitchellSmokers <- 1/(1+0.012*delayVector)
mitchellNonsmokers <- 1/(1+0.006*delayVector)

# reynoldsCurve

reynoldsCurveSmokers <- 1/(1+0.075*delayVector)
reynoldsCurveNonsmokers <- 1/(1+0.014*delayVector)

pointSize <- 1.25
lineWidth <- 1.5

minX <- 0
maxX <- 400

middleGray <- "#636363"
lightestGray <- "#cccccc"
laststGray <- "#e5e5e5"
endGray <- "#efefef"

xLab <- "Delay (Days)"
yLab <- "Value (Proportional)"

pTitle <- "Combined PB-AUC and Adjusted MB-AUC Measures"

par(family = "serif", mar=c(3,3,2,1), mgp=c(2,.7,0), tck=-.01)

plot(delays, 
     reynoldsSmokers, 
     type = 'o',
     col = 'black',
     pch = 15,
     cex = pointSize,
     cex.lab = 1.25,
     cex.axis = 1.25,
     cex.main = 0.1,
     lty = 1,
     lwd = lineWidth,
     main = NA,
     family = "serif",
     xlab = xLab,
     ylab = yLab,
     xlim = c(minX, maxX),
     ylim = c(0, 1.0))

points(delays,
       reynoldsNonSmokers,
       type = 'o',
       col = 'black',
       pch = 22,
       lty = 2,
       lwd = lineWidth,
       cex = pointSize)

lines(delayVector,
      friedelSmokers,
      type = 'l',
      col = middleGray,
      lwd = lineWidth,
      lty = 1)

lines(delayVector,
      friedelNonsmokers,
      type = 'l',
      col = middleGray,
      lwd = lineWidth,
      lty = 2)

lines(delayVector,
      bickelSmokers,
      type = 'l',
      col = lightestGray,
      lwd = lineWidth,
      lty = 1)

lines(delayVector,
      bickelNonsmokers,
      type = 'l',
      col = lightestGray,
      lwd = lineWidth,
      lty = 2)

lines(delayVector,
      mitchellSmokers,
      type = 'l',
      col = laststGray,
      lwd = lineWidth,
      lty = 1)

lines(delayVector,
      mitchellNonsmokers,
      type = 'l',
      col = laststGray,
      lwd = lineWidth,
      lty = 2)

lines(delayVector,
      reynoldsCurveSmokers,
      type = 'l',
      col = endGray,
      lwd = lineWidth,
      lty = 1)

lines(delayVector,
      reynoldsCurveNonsmokers,
      type = 'l',
      col = endGray,
      lwd = lineWidth,
      lty = 2)

legend(
  "topright", 
  bty = "n",
  lty = c(NA, 
          1, 1, 1, 1, 1,
          NA, NA,
          2, 2, 2, 2, 2), 
  lwd = rep(lineWidth, 9),
  cex = 0.75,
  text.font = c(2,1,1,1,1,1,1,2,1,1,1,1,1),
  col = c("black",
          "black", middleGray, lightestGray, laststGray, endGray,
          "black", "black", 
          "black", middleGray, lightestGray, laststGray, endGray), 
  legend = c("Smokers",
             "Reynolds et al. (2007);  PB-AUC = 0.156", 
             "Friedel et al. (2014); Myerson-Green MB-AUC = 0.167", 
             "Bickel et al. (1999); Mazur MB-AUC = 0.151", 
             "Mitchell et al. (1999); Mazur MB-AUC = 0.382",
             "Reynolds et al. (2004); Mazur MB-AUC = 0.119",
             "",
             "Nonsmokers",
             "Reynolds et al. (2007); PB-AUC = 0.323",  
             "Friedel et al. (2014); Myerson-Green MB-AUC = 0.235",
             "Bickel et al. (1999); Mazur MB-AUC = 0.486",
             "Mitchell et al. (1999); Mazur MB-AUC = 0.528",
             "Reynolds et al. (2004); Mazur MB-AUC = 0.352")
)

```

This plot illustrates the relationship between PB-AUC and MB-AUC when MB-AUC is adjusted to reflect the delays from the PB-AUC. 

